
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% A clean template for an academic CV. This is a short summary version.
%
% Uses tabularx to create two column entries (date and job/edu/citation).
% Defines commands to make adding entries simpler.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[french, 10pt, a4paper]{article}

% Full Unicode support for non-ASCII characters
\usepackage[utf8]{inputenc}
\usepackage[french]{babel}

% Identifying information
\newcommand{\Title}{Curriculum Vit\ae\   --   Résumé}
\newcommand{\FirstName}{Thomas}
\newcommand{\LastName}{Steimlé}
\newcommand{\Initials}{TS}
\newcommand{\MyName}{Dr. \FirstName\ \LastName}
\newcommand{\Me}{\textbf{\FirstName\ \LastName}}  % For citations
\newcommand{\Email}{thomas.steimle@gmail.com}
\newcommand{\ORCID}{0000-0001-6019-7288}
\newcommand{\Address}{
  Hôpital Necker Enfants Malades -- Laboratoire d'Onco-Hématologie Tour Pasteur -- 149 rue de Sèvres 75015 Paris
}
\newcommand{\PersonalWebsite}{github.com/Dr-TSteimle}


% Template configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Disable hyphenation
\usepackage[none]{hyphenat}

% Control the font size
\usepackage{anyfontsize}

% Icon fonts (requires using xelatex or luatex)
\usepackage[fixed]{fontawesome5}
\usepackage{academicons}

% Template variables for styling
\newcommand{\TablePad}{\vspace{-0.4cm}}
\newcommand{\SoftwareTitle}[1]{{\bfseries #1}}
\newcommand{\TableTitle}[1]{{\fontsize{12pt}{0}\selectfont \itshape #1}}

% For fancy and multipage tables
\usepackage{tabularx}
\usepackage{ltablex}

% Define a new environment to place all CV entries in a 2-column table.
% Left column are the dates, right column the entries.
\usepackage{environ}
\NewEnviron{EntriesTable}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.10\textwidth}@{\hspace{0.02\textwidth}}p{0.88\textwidth}@{}}
  \BODY
\end{tabularx}
}

\NewEnviron{EntriesTable2}{
\TablePad
\begin{tabularx}{\textwidth}{@{}p{0.10\textwidth}@{\hspace{0.02\textwidth}}p{0.25\textwidth}@{\hspace{0.02\textwidth}}p{0.6\textwidth}@{}}
  \BODY
\end{tabularx}
}

% Macros to add links and mark publications
\newcommand{\DOI}[1]{doi:\href{https://doi.org/#1}{#1}}
\newcommand{\DOILink}[1]{\href{https://doi.org/#1}{doi.org/#1}}
\newcommand{\Website}[1]{\href{https://#1}{#1}}
\newcommand{\Preprint}[1]{\newline Preprint: \faFilePdf\ \DOILink{#1}}
\newcommand{\Youtube}[1]{\newline Recording: \faYoutube\, \href{https://www.youtube.com/watch?v=#1}{youtube.com/watch?v=#1}}
\newcommand{\GitHub}[1]{\faGithub\ \href{https://github.com/#1}{github.com/#1}}
\newcommand{\Role}[1]{\newline Role: \faUsers\ #1}
\newcommand{\Slides}[1]{\newline Slides: \faTv\ \href{https://#1}{#1}}
\newcommand{\SlidesDOI}[1]{\newline Slides: \faTv\ \DOILink{#1}}
\newcommand{\PosterDOI}[1]{\newline Poster: \faImage\ \DOILink{#1}}
\newcommand{\OA}{\aiOpenAccess}

% Macros to set the year and duration on the left column
\newcommand{\Duration}[2]{\fontsize{9pt}{0}\selectfont #1 -- #2}
\newcommand{\Year}[1]{\fontsize{9pt}{0}\selectfont #1}
\newcommand{\Ongoing}{act.}
\newcommand{\Future}{future}
\newcommand{\Appointment}[4]{\textbf{#1} \newline #2 \newline #3 \newline #4}

% Define command to insert month name and year as date
\usepackage{datetime}
\newdateformat{monthyear}{\monthname[\THEMONTH], \THEYEAR}

% Set the page margins
\usepackage[a4paper,margin=1.5cm,includehead,headsep=5mm]{geometry}

% To get the total page numbers (\pageref{LastPage})
\usepackage{lastpage}

% No indentation
\setlength\parindent{0cm}

% Increase the line spacing
\renewcommand{\baselinestretch}{1.2}
% and the spacing between rows in tables
\renewcommand{\arraystretch}{1.2}

% Remove space between items in itemize and enumerate
\usepackage{enumitem}
\setlist{nosep}

% Use custom colors
\usepackage[usenames,dvipsnames]{xcolor}

% Set fonts (requires compilation with xelatex)

\usepackage{fontspec}
\setmonofont{FiraSans}[
  Contextuals=Alternate  % Activate the calt feature
]

% Set the spacing for sections
\usepackage{titlesec}
\titleformat{\section}
  {\normalfont\large\mdseries} % format
  {} % label
  {0pt} % separation (left separation for hang)
  {} % text before title
  [\titlerule] % text after title
\titleformat{\subsection}
  {\normalfont\mdseries} % format
  {} % label
  {0pt} % separation (left separation for hang)
  {} % text before title

% Disable number of sections. Use this instead of "section*" so that the sections still
% appear as PDF bookmarks. Otherwise, would have to add the table of contents entries
% manually.
\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

% Set fancy headers
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{\fontsize{9pt}{10pt}\selectfont
  \monthyear\today
}
\chead{
  \fontsize{9pt}{10pt}\selectfont
  \MyName
  \hspace{0.2cm} -- \hspace{0.2cm}
  \Title
}
\rhead{\fontsize{9pt}{10pt}\selectfont \thepage{} of \pageref*{LastPage}}
\renewcommand{\headrulewidth}{0pt}

% Metadata for the PDF output and control of hyperlinks
\usepackage[colorlinks=true]{hyperref}
\hypersetup{
  pdftitle={\MyName\ - \Title},
  pdfauthor={\MyName},
  linkcolor=blue,
  citecolor=blue,
  filecolor=black,
  urlcolor=MidnightBlue
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% No header for the first page
\thispagestyle{empty}

% Remove extra header space
\vspace*{-2.75\baselineskip}

\begin{minipage}[t]{0.7\textwidth}
  {\fontsize{16pt}{0}\selectfont\MyName}
\end{minipage}
\begin{minipage}[t]{0.3\textwidth}
  \begin{flushright}
    \monthyear\today
  \end{flushright}
\end{minipage}
\\[-0.1cm]
\rule{\textwidth}{1pt}
\vspace{-0.75cm}
\begin{center}
  Email: \href{mailto:\Email}{\Email} |
  ORCID: \href{https://orcid.org/\ORCID}{\ORCID} |
  Website: \Website{\PersonalWebsite}
  \\
  \Address
\end{center}
\vspace{-0.5cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\begin{EntriesTable}
  \Duration{2022}{\Ongoing}  &
  \textbf{PhD in Biosciences and Bioinformatics}, TAGC Inserm U1090 (Marseille), ``Normal and Pathological Hematopoiesis'' at Inserm U1151 (Paris)
  \textit{``Integrative genomics to unravel meaningful and targetable regulatory pathways for personalized treatment of t-cell acute lymphoblastic leukemia.''}
  \\
  \Duration{2019}{2020}  &
  \textbf{Master of Science}, Oncology specialization track (Paris-Saclay University)
  % \textbf{MSc in Geophysics}
  \\
  \Duration{2012}{2016}  &
  \textbf{MD in Pathology-Biology} (Université de Dijon), MD thesis: \textit{``Identification de mutations ponctuelles dans les lymphomes B diffus à grandes cellules.''}
  % \textbf{MD in Pathology}
  % \\
  % \Duration{2012}{2016}  &
  % \textbf{Diplôme d'études Spécialisées de Biologie Médicale option Biologie Spécialisée en Hématologie} (Université de Dijon)
  \\
  \Duration{2014}{2015}  &
  \textbf{University degree} Hematological cytology (Bourgogne-Franche-Comté University)
  \\
  \Duration{2013}{2014}  &
  \textbf{University degree} Laboratory quality management system ``Formation aux normes de qualité en vigueur applicables aux laboratoires de biologie médicale`` (Sorbonne University, Pierre and Marie Curie Campus)
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experience}

\begin{EntriesTable}
  \Duration{2022}{\Ongoing}  &
  \textbf{PhD student}, TAGC Inserm U1090 (Marseille), Hématopoïèse normale et pathologique Inserm U1151 (Paris)
  \\
  \Duration{2018}{2022}  &
  \textbf{Assistant -- Junior Doctor}, Hôpital Necker Enfants Malades (Paris), Onco-Hematology Laboratory
  \\
  \Duration{2016}{2018}  &
  \textbf{Assistant -- Junior Doctor}, Institut Gustave Roussy (Villejuif), Hematology Laboratory
  \\
  \Duration{2012}{2016}  &
  \textbf{Resident in Medical Biology -- Pathology}, Hôpital Universitaire du Bocage (Dijon)
  \\
  \Duration{2009}{2012}  &
  \textbf{Medical student (extern) and Nursing Assistant}, Hôpitaux Universitaires de Strasbourg
\end{EntriesTable}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Grant}

\begin{EntriesTable}
  \Duration{2022}{\Ongoing}  &
  \textbf{PhD position for medical residents and junior doctors}, Fondation pour la Recherche Médicale (FRM) for
  \textit{``Integrative genomics to unravel meaningful and targetable regulatory pathways for personalized treatment of t-cell acute lymphoblastic leukemia.''}
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Academic Service}

% \begin{EntriesTable}
%   \Duration{2019}{\Ongoing} & Topic editor, \textit{Journal of Open Source Software}
%   \\
%   \Duration{2021}{\Ongoing} & Code of Conduct Working Group, \textit{Software Underground}
%   \\
%   \Duration{2019}{\Ongoing} & Advisory Council, \textit{EarthArXiv}
% \end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Teaching}
% \section{Current Teaching}

\begin{EntriesTable}
  \Duration{2019}{2022}  &
  \textbf{Teaching assistant}, Practical sessions in hematology for students in the second cycle of medical studies at the University of Paris.
  \\
  \Duration{2018}{2022}  &
  \textbf{Courses for medical students} during their internship at the onco-hematology laboratory.
  \\
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}
% \section{Publication Highlights}

\begin{EntriesTable}
\Year{2022}  &
  \Me, Marie-Emilie Dourthe, Marion Alcantara, Aurore Touzart, Mathieu Simonin, Johanna Mondesir, Jonathan Bond, 
  Carlos Graux, Nathalie Grardel, Jean-Michel Cayuela, Isabelle Arnoux, Virginie Gandemer, Marie Balsat, 
  Norbert Vey, Elizabeth Macintyre, Norbert Ifrah, Hervé Dombret, Arnaud Petit, André Baruchel, 
  Philippe Ruminy, Nicolas Boissel \& Vahid Asnafi.
  Clinico-biological features of T-cell acute lymphoblastic leukemia with fusion proteins
  \emph{Blood Cancer Journal}.
  \DOI{10.1038/s41408-022-00613-9}{ }\OA
  \\
\Year{2022}  &
  Estelle Balducci, Sophie Kaltenbach, Patrick Villarese, Eugénie Duroyon, Loria Zalmai, Chloé Friedrich, Felipe Suarez, Ambroise Marcais, Didier Bouscary, Justine Decroocq, Rudy Birsen, Michaëla Fontenay, Marie Templé, Chantal Brouzes, Aurore Touzart, \Me, Agata Cieslak, Ludovic Lhermitte, Carole Almire, Nicolas Chapuis, Olivier Hermine, Vahid Asnafi, Olivier Kosmider \& Lucile Couronné.
  Pooch: A friend to fetch your data files.
  \emph{Blood Cancer Journal}.
  \DOI{10.1038/s41408-022-00718-1}{ }\OA
  \\
\Year{2021}  &
  Nabih Maslah, Mehdi Latiri, Vahid Asnafi, Mélanie Féroul, Nawel Bedjaoui, \Me, Emmanuelle Six, Els Verhoyen, Elizabeth Macintyre, Chantal Lagresle-Peyrou, Guillaume P. Andrieu.
  Adenylate kinase 2 expression and addiction in T-ALL
  \emph{Blood Advances}.
  \DOI{10.1182/bloodadvances.2020002700}{ }\OA
  \\
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open Science}

\begin{EntriesTable}
  \Year{2023} &
  \textbf{SV Finder} | \GitHub{Dr-TSteimle/sv-finder}
  \newline
  Software for detection and characterization of structural variants in massively parallel sequencing data.
  \\
\end{EntriesTable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data Science}

\begin{EntriesTable2}
  & \textbf{Programming languages} & \hspace{.3cm}\faRProject R \faRust Rust \faPython Python \faJs Javascript LaTeX \\
  & \textbf{\newline Projects} 
  & \begin{itemize}
      \item Implementation of a pipeline for detecting insertions sites of
      HTLV1 in human genome NGS data.
      \item NGS Exome analysis (alterations and CNV) of mantle cell
      lymphomas.
      \item NGS Exome analysis fo CLOVES syndrome samples (very low
      VAF) with amplicon panel confirmation.
      \item Software development for finding structural variants
      in targeted NGS data (TCR\delta{ }translocations, cf. SV finder).
    \end{itemize}
\end{EntriesTable2}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Laboratory}

\begin{EntriesTable2}
  & \textbf{\newline Skills} 
  & \begin{itemize}
      \item Optical Microscopy, expert in bone marrows, blood and liquids diagnosis in hematology (100+ diagnosis performed).
      \item Flow Cytometry preparation and analysis for diagnosis, MRD and experiments (R, flowjo, BD).
      \item NGS target panels and exomes, from design to analysis.
      \item Longreads sequencing, implementation, development and analysis.
      \item PCR (Q and RT) from design to analysis.
      \item Cell culture, drug testing with synergy analysis.
      \item Different kinds of benchtop automated system.
    \end{itemize}
\end{EntriesTable2}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Language Skills}

\begin{EntriesTable2}
  & \textbf{French} & \hspace{.3cm} Native\\
  & \textbf{English} & \hspace{.3cm} Full professional proficiency scientific and medical (C2)\\
  & \textbf{German \& Spanish} & \hspace{.3cm} Intermediate (B2)\\
\end{EntriesTable2}

\end{document}